### 2022-11-25 draft_final_assingment.Rmd
Add files via upload

---
title: "junk_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
```

```{r}
url <- "https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/dummy_df.csv"

df <- read_csv(url)
```

## Cleaning data
```{r}
#Trying to extract party name (D or R) from the sponsor, will figure this out with Regex

df %>%
  mutate(party = ifelse(str_detect(Sponsor, "[R-"), "Republican", 
                   ifelse(str_detect(Sponsor, "[D-"), "Democrat", NA)))
```

## Creating document feature matrix
```{r}
dfmat <- df$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()
```

## Most common words
```{r}
#Overall most common words

tfreq <- dfmat %>%
  textstat_frequency() %>%
  head(20)

tfreq$feature <- factor(tfreq$feature, levels=tfreq$feature)

ggplot(tfreq, aes(x=frequency, y=feature)) +
geom_col() + 
  theme_minimal()
```

```{r}
# Most common words by Congressional sesson
df_116 <- df %>%
  filter(Congress == "116")

df_117 <- df %>%
  filter(Congress == "117")

dfmat_116 <- df_116$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

dfmat_117 <- df_117$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature) 
tfreq_117$feature <- factor(tfreq_117$feature, levels=tfreq_117$feature)

p116 <- ggplot(tfreq_116, aes(x=frequency, y=feature)) +
  geom_col() + 
  theme_minimal()

p117 <- ggplot(tfreq_117, aes(x=frequency, y=feature)) +
  geom_col() + 
  theme_minimal()

p116
```

```{r}
p117
```

```{r}
df$era <- ifelse(df$Congress == 116, "Pre", "Post")

ytfreq <- dfmat %>% 
  textstat_frequency(groups = df$era) %>%
  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)

ggplot(ytfreq, aes(x="Post", y="Pre")) + 
  geom_point() +
  coord_fixed()
```
```{r}
sims <- textstat_simil(dfmat, method="cosine")

sim_df <- as.data.frame(sims, upper = TRUE)

sim_df
```
```{r}
library(uwot)

corp <- corpus(df$Summary)

dfmat2 <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm() %>%
  dfm_trim(min_termfreq = 5)

embeddings <- umap(as.matrix(dfmat2))

df$x <- embeddings[,1]
df$y <- embeddings[,2]

colordict <- c( "Labour"="red","LibDems"="yellow", "Conservatives"="Blue","Greens"="green")

p <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) + theme_bw() +
  coord_fixed()

p
```

```{r}
library(topicmodels) 
lda <- LDA(dfmat, 3)

lda
```
```{r}
library(tidytext)

topic_words <- tidy(lda, matrix="beta") %>% 
  group_by(topic) %>%
  slice_max(beta, n = 3) %>%
  ungroup() %>%
  arrange(topic, -beta)

topic_words

topic_words %>%
  mutate(term = reorder_within(term, beta, topic)) %>% 
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") + scale_y_reordered()
```

##Sentiments
```{r}
lex <- get_sentiments("afinn")

text_tokens <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))

doc_sentiments
```

```{r}
library(vader)

sentiments <- vader_df(df$Summary)

summary_sentiment <- cbind(df, select(sentiments,-text))

pos <- summary_sentiment %>% 
  arrange(desc(compound)) %>% 
  head()

for( i in rownames(pos) ) { 
  print(pos[i, "text"]) 
  print(pos[i, "compound"])
}

neg <- summary_sentiment %>% 
  arrange(compound) %>% 
  head()

for( i in rownames(neg) ) { 
  print(neg[i, "text"]) 
  print(neg[i, "compound"])
}
```

### 2022-11-25 multi_thread_script.py
data push

@@ -87,6 +87,7 @@ def get_root_url(url):
 
 def loop_function(api_key, url):
     try:
+
             metadata = get_congress_data(get_root_url(url), api_key=api_key)
             # TODO: get infos from metadata dictionary, like sponsors, originChamber, polyArea, title
             
@@ -117,59 +118,63 @@ def loop_function(api_key, url):
                     
             latest_action = metadata['bill']['latestAction']['actionDate']
             
-            summary_l = get_congress_data(get_root_url(url) + '/summaries', api_key=api_key)['summaries']
-            
-            summary_dict = {i['actionDesc']: i['text'] for i in summary_l}
-            
-            summary_dict['bill'] = bill_number
-            summary_dict['title'] = metadata['bill']['title']
-            
             subjects = get_congress_data(get_root_url(url) + '/subjects', api_key=api_key)['subjects']
             
-            related_bills = get_congress_data(get_root_url(url) + '/relatedbills', api_key=api_key)
+            # related_bills = get_congress_data(get_root_url(url) + '/relatedbills', api_key=api_key)
             
-            # dic_i = {'metadata': metadata,
-            # 'text' : text,
-            # 'summary': summary,
-            # 'subjects': subjects,
-            # 'related_bills': related_bills
-            # }
-            
-            try:
+            # try:
                     
-                    text_l = get_congress_data(get_root_url(url) + '/text', api_key=api_key)['textVersions']
+            #         text_l = get_congress_data(get_root_url(url) + '/text', api_key=api_key)['textVersions']
                     
-                    if len(text_l) > 2:
+            #         if len(text_l) > 2:
                             
-                            text_dict = {i['type']: get_bill_text(i['formats'][0]['url']) for i in text_l if (i['formats'] and i['type'])}
-                    else:
-                            text_dict = {text_l[0]['type']: get_bill_text(text_l[0]['formats'][0]['url'])}
+            #                 text_dict = {i['type']: get_bill_text(i['formats'][0]['url']) for i in text_l if (i['formats'] and i['type'])}
+            #         else:
+            #                 text_dict = {text_l[0]['type']: get_bill_text(text_l[0]['formats'][0]['url'])}
                     
-                    text_dict['bill'] = row['number']
[…]

### 2022-11-27 draft_final_assingment.Rmd
Parties are now within the dataset
Wordclouds for congresses and parties

@@
 library(readr)
+library(dplyr)
+library(quanteda.textplots)
 ```
@@
 
-df %>%
-  mutate(party = ifelse(str_detect(Sponsor, "[R-"), "Republican", 
-                   ifelse(str_detect(Sponsor, "[D-"), "Democrat", NA)))
+df$party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
+```
+
+## Creating a corpus
+```{r}
+df_corp <- df
+df_corp <- df_corp %>% rename(text = Summary)
+corp <- corpus(df_corp)
+
+````
+
+##Creatung a dfm from the corpus
+```{r}
+dfm <- corp %>%
+  tokens(remove_punct = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  dfm()
+
+````
+
+##Most common words in the corpus
+```{r}
+
+dfm %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+```
+
+#Wordcloud comparing Democrats and Republicans
+```{r}
+dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
+    dfm_trim(min_termfreq = 3)
+
+textplot_wordcloud(dfmat2, comparison = TRUE, max_words = 300,
+                   color = c("blue", "red"))
+
+```
+
+#Wordcloud comparing Congress
+```{r}
+dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
+    dfm_trim(min_termfreq = 3)
+
+textplot_wordcloud(dfmat3, comparison = TRUE, max_words = 300,
+                   color = c("blue", "red"))
+
 ```

### 2022-11-27 draft_final_assingment.Rmd
More wordclouds

@@
 
+#Wordcloud congress 116
+
+```{r}
+dfmat4 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
+    dfm_trim(min_termfreq = 1)
+
+textplot_wordcloud(dfmat4, max_words = 300)
+
+```
+
+#Wordcloud congress 117
+
+```{r}
+dfmat5 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
+    dfm_trim(min_termfreq = 1)
+
+textplot_wordcloud(dfmat5, max_words = 300)
+
+```
+
 #Wordcloud comparing Democrats and Republicans
@@
 
-#Wordcloud comparing Congress
+#Wordcloud comparing Congresses
 ```{r}

### 2022-11-27 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 
-df$party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
+df$Party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
 ```
@@
 ```{r}
-dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
+dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
     dfm_trim(min_termfreq = 3)

### 2022-11-27 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

--- 2022-11-27 draft_final_assingment.Rmd
@@
 ```{r}
-dfm <- corp %>%
+dfm_corp <- corp %>%
   tokens(remove_punct = TRUE) %>%
@@
 
-dfm %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+```
+
+#Wordcloud congress 116
+
+```{r}
+dfmat116 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
+    dfm_trim(min_termfreq = 1)
+
+textplot_wordcloud(dfmat116, max_words = 300)
+
+```
+
+#Wordcloud congress 117
+
+```{r}
+dfmat117 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
+    dfm_trim(min_termfreq = 1)
+
+textplot_wordcloud(dfmat117, max_words = 300)
+
 ```
@@
 ```{r}
-dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
+dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
     dfm_trim(min_termfreq = 3)
 
-textplot_wordcloud(dfmat2, comparison = TRUE, max_words = 300,
+textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                    color = c("blue", "red"))
@@
 
-#Wordcloud comparing Congress
+#Wordcloud comparing Congresses
 ```{r}
-dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
+dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
     dfm_trim(min_termfreq = 3)
 
-textplot_wordcloud(dfmat3, comparison = TRUE, max_words = 300,
+textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                    color = c("blue", "red"))

### 2022-11-27 cleaning_html_data.Rmd
Add files via upload

---
title: "Cleaning HTLM Tags"
author: "Andrew Wells"
date: "11/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r}
library(tidyverse)
library(quanteda)
library(readr)
```

#Loading data
```{r}
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/all_data.csv")
```

## Cleaning data
```{r}
#Function for removing HTML tags
cleanFun <- function(htmlString) {
  return(gsub("<.*?>", "", htmlString))
}

#Applying function to clean data
df$summary <- cleanFun(df$summary)
```

#Saving data
```{r}
write.csv(df, "~/Desktop/Semester 5/Classes/4. Text as data/Assignments/Final assignment/all_data_cleaned_summary.csv")
```

### 2022-11-28 Presentation Congressional Data.qmd

---
title: "US Congress Data"
format: revealjs
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished presentation. To learn more about Quarto presentations see <https://quarto.org/docs/presentations/>.

## Bullets

When you click the **Render** button a document will be generated that includes:

-   Content authored with markdown
-   Output from executable code

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

## Our first steps

ewjfnweögnw

WEFÖGNwegoin

WEGOINW\$GOIErn

```{r}
#our code
```

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 ```{r}
-url <- "https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/dummy_df.csv"
+
+url <- "data/data_11_28.csv"
 
@@
 df_corp <- df
-df_corp <- df_corp %>% rename(text = Summary)
+df_corp <- df_corp %>% rename(text = summary)
 corp <- corpus(df_corp)
@@
 dfm_corp <- corp %>%
-  tokens(remove_punct = TRUE) %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
   tokens_remove(patter = stopwords("en")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
   dfm()

### 2022-11-28 draft_final_assingment.Rmd
cleaning_file

--- 2022-11-27 draft_final_assingment.Rmd
@@
 ---
-title: "junk_final_assignment"
+title: "draft_final_assignment"
 author: "Andrew Wells"
@@
 
-```{r}
-url <- "https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/dummy_df.csv"
-
-df <- read_csv(url)
+```{r }
+df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
+```
+## Creating a corpus
+```{r }
+df_corp <- df
+df_corp <- df_corp %>% rename(text = summary)
+corp <- corpus(df_corp)
 ```
 
-## Cleaning data
-```{r}
-#Trying to extract party name (D or R) from the sponsor, will figure this out with Regex
-
-df$Party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
+##Creatung a dfm from the corpus
+```{r }
+dfm_corp <- corp %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
+  dfm()
 ```
-
-## Creating a corpus
-```{r}
-df_corp <- df
-df_corp <- df_corp %>% rename(text = Summary)
-corp <- corpus(df_corp)
-
-````
-
-##Creatung a dfm from the corpus
-```{r}
-dfm_corp <- corp %>%
-  tokens(remove_punct = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  dfm()
-
-````
 

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 library(quanteda.textplots)
+library(uwot)
+library(topicmodels)
 ```
@@
   tokens_remove(patter = stopwords("en")) %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
   dfm()
+
+#Do we also want to lemmatize and apply word stems??
+
+# tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
+
+# tokens_wordstem() %>%
 ```
@@
 ##Most common words in the corpus
-```{r}
+```{r }
+dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+```
+#Wordcloud congress 115
 
-dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+```{r }
+dfmat115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
+                remove_numbers = TRUE) %>%
+  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+    dfm_trim(min_termfreq = 1)
+
+textplot_wordcloud(dfmat115, max_words = 300)
 ```
@@
 
-```{r}
-dfmat116 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
+```{r }
+dfmat116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
+                remove_numbers = TRUE) %>%
+  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
     dfm_trim(min_termfreq = 1)
@@
 textplot_wordcloud(dfmat116, max_words = 300)
-
 ```
@@
 
-```{r}
-dfmat117 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
+```{r }
+dfmat117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
+                remove_numbers = TRUE) %>%
+  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
     dfm_trim(min_termfreq = 1)
@@
 textplot_wordcloud(dfmat117, max_words = 300)
-
 ```
@@
 #Wordcloud comparing Democrats and Republicans
-```{r}
+```{r }
+#Need to get sponser party data
+
 dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
@@
 #Wordcloud comparing Congresses
-```{r}
+```{r }
 dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
@@
 
-## Creating document feature matrix
-```{r}
-dfmat <- df$Summary %>%
-  tokens(remove_punct = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  dfm()
-```
-
-## Most common words
+## Most common words (overall)
 ```{r}
@@
 
-tfreq <- dfmat %>%
+tfreq <- dfm_corp %>%
   textstat_frequency() %>%
@@
 ggplot(tfreq, aes(x=frequency, y=feature)) +
-geom_col() + 
+geom_col() + labs(title="Feature (word) frequency",
+        x ="Frequency", y = "Feature") +
+  theme_minimal() 
+```
+## Most common words (by session)
+
+```{r }
+# Most common words by Congressional session 115
+df_115 <- df %>%
+  filter(session == "115")
+
+dfmat_115 <- df_115$summary %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm()
+
+tfreq_115 <- dfmat_115 %>%
+  textstat_frequency() %>%
+  head(20)
+
+tfreq_115$feature <- factor(tfreq_115$feature, levels=tfreq_115$feature)
+
+ggplot(tfreq_115, aes(x=frequency, y=feature)) +
+  geom_col() + labs(title="Feature (word) frequency for 115 session (2017 - 2018)",
+        x ="Frequency", y = "Feature") +
   theme_minimal()
@@
 
-```{r}
-# Most common words by Congressional sesson
+```{r }
+# Most common words by Congressional session 116
 df_116 <- df %>%
-  filter(Congress == "116")
+  filter(session == "116")
 
-df_117 <- df %>%
-  filter(Congress == "117")
-
-dfmat_116 <- df_116$Summary %>%
-  tokens(remove_punct = TRUE) %>%
+dfmat_116 <- df_116$summary %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
   tokens_remove(patter = stopwords("en")) %>%
-  dfm()
-
-dfmat_117 <- df_117$Summary %>%
-  tokens(remove_punct = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
   dfm()
@@
 
+tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature)
+
+ggplot(tfreq_116, aes(x=frequency, y=feature)) +
+  geom_col() + labs(title="Feature (word) frequency for 116 session (2019 - 2020)",
+        x ="Frequency", y = "Feature") +
+  theme_minimal()
+```
+
+```{r}
+# Most common words by Congressional session 117
+df_117 <- df %>%
+  filter(session == "117")
+
+dfmat_117 <- df_117$summary %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm()
+
 tfreq_117 <- dfmat_117 %>%
@@
 
-tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature) 
 tfreq_117$feature <- factor(tfreq_117$feature, levels=tfreq_117$feature)
 
-p116 <- ggplot(tfreq_116, aes(x=frequency, y=feature)) +
-  geom_col() + 
+ggplot(tfreq_117, aes(x=frequency, y=feature)) +
+  geom_col() + labs(title="Feature (word) frequency for 117 session (2021 - 2022)",
+        x ="Frequency", y = "Feature") +
   theme_minimal()
-
-p117 <- ggplot(tfreq_117, aes(x=frequency, y=feature)) +
-  geom_col() + 
-  theme_minimal()
-
-p116
 ```
@@
 ```{r}
-p117
-```
+df$era <- ifelse(df$session == 116, "Pre", "Post")
 
-```{r}
-df$era <- ifelse(df$Congress == 116, "Pre", "Post")
-
-ytfreq <- dfmat %>% 
+ytfreq <- dfm_corp %>% 
   textstat_frequency(groups = df$era) %>%
@@
 ```
+
 ```{r}
-sims <- textstat_simil(dfmat, method="cosine")
+sims <- textstat_simil(dfm_corp, method="cosine")
 
@@
 ```
-```{r}
-library(uwot)
 
-corp <- corpus(df$Summary)
+```{r }
+df <- df %>%
+  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
+                       ifelse(cosponsor_D_perc < 0.5,"Rep",
+                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))
+
+corp <- corpus(df$summary)
 
@@
 
-colordict <- c( "Labour"="red","LibDems"="yellow", "Conservatives"="Blue","Greens"="green")
+colordict <- c( "Dem"="blue","Rep"="red", "Neutral"="yellow")
 
-p <- ggplot(df, aes(x, y, fill=party)) + 
+p <- ggplot(df, aes(x, y, fill=partisan)) + 
   geom_point(color="grey", shape=21, size=0.5) + 
-  scale_fill_manual(values=colordict) + theme_bw() +
+  scale_fill_manual(values=colordict) +
+  theme_bw() +
   coord_fixed()
@@
 
-```{r}
-library(topicmodels) 
+##Topic modeling
+
+```{r }
 lda <- LDA(dfmat, 3)
@@
 ```
+
 ```{r}
@@
 
-text_tokens <- tidy(dfmat) %>% 
+text_tokens <- tidy(dfm_corp) %>% 
   inner_join(lex, by=c("term" = "word"))
 
-doc_sentiments <- tidy(dfmat) %>% 
+doc_sentiments <- tidy(dfm_corp) %>% 
   inner_join(lex, by=c("term" = "word")) %>% 

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 library(topicmodels)
+library(tidytext)
 ```
@@
 ```{r }
-lda <- LDA(dfmat, 3)
+lda <- LDA(dfm_, 3)
 

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 
-```{r}
+```{r }
 library(tidyverse)
@@
 library(tidytext)
+library(ggrepel)
 ```
@@
 ```{r }
-dfm_corp <- corp %>%
+dfmat <- corp %>%
   tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
@@
 ```{r }
-dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
+dfmat %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
 ```
@@
 ```{r }
-dfmat115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
+dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                 remove_numbers = TRUE) %>%
@@
 
-textplot_wordcloud(dfmat115, max_words = 300)
+textplot_wordcloud(dfmat_115, max_words = 300)
 ```
@@
 ```{r }
-dfmat116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
+dfmat_116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
                 remove_numbers = TRUE) %>%
@@
 
-textplot_wordcloud(dfmat116, max_words = 300)
+textplot_wordcloud(dfmat_116, max_words = 300)
 ```
-
 #Wordcloud congress 117
@@
 ```{r }
-dfmat117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
+dfmat_117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
                 remove_numbers = TRUE) %>%
@@
 
-textplot_wordcloud(dfmat117, max_words = 300)
+textplot_wordcloud(dfmat_117, max_words = 300)
 ```
@@
 ```{r }
-#Need to get sponser party data
+#Need to get sponsor party data
 
@@
 
-tfreq <- dfm_corp %>%
+tfreq <- dfmat %>%
   textstat_frequency() %>%
@@
 # Most common words by Congressional session 115
-df_115 <- df %>%
-  filter(session == "115")
-
-dfmat_115 <- df_115$summary %>%
-  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm()
-
 tfreq_115 <- dfmat_115 %>%
@@
 # Most common words by Congressional session 116
-df_116 <- df %>%
-  filter(session == "116")
-
-dfmat_116 <- df_116$summary %>%
-  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm()
-
 tfreq_116 <- dfmat_116 %>%
@@
 # Most common words by Congressional session 117
-df_117 <- df %>%
-  filter(session == "117")
-
-dfmat_117 <- df_117$summary %>%
-  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm()
-
 tfreq_117 <- dfmat_117 %>%
@@
 
+##Comparing subgroups
 ```{r}
-df$era <- ifelse(df$session == 116, "Pre", "Post")
+df <- df %>%
+  mutate(session_written = ifelse(session == 115, "session_115", 
+                             ifelse(session == 116, "session_116",
+                             ifelse(session == 117, "session_117", NA))))
 
-ytfreq <- dfm_corp %>% 
-  textstat_frequency(groups = df$era) %>%
+ytfreq <- dfmat %>% 
+  textstat_frequency(groups = df$session_written) %>%
   pivot_wider(id_cols=feature, names_from=group, values_from=frequency)
+```
 
-ggplot(ytfreq, aes(x="Post", y="Pre")) + 
-  geom_point() +
-  coord_fixed()
+```{r}
+#Comparing sessions 115 and 116
+
+#Plot #1: differences in frequency by session
+ggplot(ytfreq, aes(x= session_116, y= session_115)) + 
+  geom_point() + theme_minimal()
+
+#Plot #2: coloring changes by session
+ytfreq$change_115_116 <- log(ytfreq$session_116 / ytfreq$session_115)
+max_change <- max(abs(ytfreq$change_115_116), na.rm=TRUE)
+
+ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
+  geom_point(color="grey", shape=21) +
+  scale_fill_gradientn(
+    colors = c("#4575b4","white","#d73027"),
+    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
+theme_bw()
+
+#Plot 3: labeling words with biggest change
+labels <- ytfreq %>% 
+  rowwise() %>% 
+  mutate(max_value = max(session_116, session_115)) %>% 
+  filter((abs(change_115_116)>0.4 & max_value>2.5) )
+
+ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
+  geom_point(color="grey", shape=21) +
+  scale_fill_gradientn(
+    colors = c("#4575b4","white","#d73027"),
+    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
+  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
+```
+
+```{r}
+#Comparing sessions 116 and 117
+ggplot(ytfreq, aes(x= session_117, y= session_116)) + 
+  geom_point() + theme_minimal()
+
+#Plot #2: coloring changes by session
+ytfreq$change_116_117 <- log(ytfreq$session_117 / ytfreq$session_116)
+max_change <- max(abs(ytfreq$change_116_117), na.rm=TRUE)
+
+ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
+  geom_point(color="grey", shape=21) +
+  scale_fill_gradientn(
+    colors = c("#4575b4","white","#d73027"),
+    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
+theme_bw()
+
+#Plot 3: labeling words with biggest change
+labels <- ytfreq %>% 
+  rowwise() %>% 
+  mutate(max_value = max(session_117, session_116)) %>% 
+  filter((abs(change_116_117)>0.4 & max_value>2.5) )
+
+ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
+  geom_point(color="grey", shape=21) +
+  scale_fill_gradientn(
+    colors = c("#4575b4","white","#d73027"),
+    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
+  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
 ```

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 library(ggrepel)
+library(vader)
+Library(tidyr)
 ```
@@
 ```{r }
-lda <- LDA(dfm_, 3)
+#Topics for session 115 (2017 - 2018)
 
-lda
-```
+lda_115 <- LDA(dfmat_115, 5)
 
-```{r}
-library(tidytext)
-
-topic_words <- tidy(lda, matrix="beta") %>% 
+topic_words_115 <- tidy(lda_115, matrix="beta") %>% 
   group_by(topic) %>%
-  slice_max(beta, n = 3) %>%
+  slice_max(beta, n = 10) %>%
   ungroup() %>%
@@
 
-topic_words
+topic_words_115
 
-topic_words %>%
+topic_words_115 %>%
   mutate(term = reorder_within(term, beta, topic)) %>% 
@@
   geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free") + scale_y_reordered()
+  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
+```
+
+```{r }
+#Topics for session 116 (2019 - 2020)
+
+lda_116 <- LDA(dfmat_116, 5)
+
+topic_words_116 <- tidy(lda_116, matrix="beta") %>% 
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+topic_words_116
+
+topic_words_116 %>%
+  mutate(term = reorder_within(term, beta, topic)) %>% 
+  ggplot(aes(beta, term, fill = factor(topic))) + 
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
+```
+
+```{r }
+#Topics for session 117 (2021 - 2022)
+raw.sum = apply(dfmat_117,1,FUN=sum) #Removing non-0 rows from dfmat
+dfmat_117 = dfmat_117[raw.sum != 0, ]
+
+lda_117 <- LDA(dfmat_117, 5)
+
+topic_words_117 <- tidy(lda_117, matrix="beta") %>% 
+  group_by(topic) %>%
+  slice_max(beta, n = 10) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+topic_words_117
+
+topic_words_117 %>%
+  mutate(term = reorder_within(term, beta, topic)) %>% 
+  ggplot(aes(beta, term, fill = factor(topic))) + 
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
 ```
@@
 
-text_tokens <- tidy(dfm_corp) %>% 
+text_tokens <- tidy(dfmat) %>% 
   inner_join(lex, by=c("term" = "word"))
 
-doc_sentiments <- tidy(dfm_corp) %>% 
+doc_sentiments <- tidy(dfmat) %>% 
   inner_join(lex, by=c("term" = "word")) %>% 
@@
 ```{r}
-library(vader)
+df %>%
+  is.na(summary)
 
-sentiments <- vader_df(df$Summary)
+sentiments <- vader_df(df$summary)
 
@@
 ```
+
+```{r}
+library(tidyr)
+#tweet_sentiment$date <- as.Date(tweet_sentiment$created)
+
+wide_sentiment <- summary_sentiment %>%
+  group_by(partisan, date) %>%
+  summarise(score = mean(compound)) %>% 
+  pivot_wider(names_from = partisan, values_from = score)
+
+days <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2022-12-31"),1))
+
+daily_sentiment <- days %>% 
+  left_join(wide_sentiment) %>% 
+  pivot_longer(cols = -date, names_to="partisan", values_to="score") %>% 
+  group_by(partisan) %>% 
+  arrange(date) %>%
+  mutate(score7 = data.table::frollmean(score, 7))
+
+daily_sentiment %>% head()
+
+ggplot(daily_sentiment, aes(date, colour=partisan)) +
+  geom_point(aes(y=score),size=0.5) + geom_line(aes(y=score7))
+```

### 2022-11-28 draft_final_assingment.Rmd
r_updates

@@
 library(vader)
-Library(tidyr)
+library(tidyr)
 ```
@@
 ```{r}
-df %>%
-  is.na(summary)
+#Loading df with VADER compount scores
 
-sentiments <- vader_df(df$summary)
-
-summary_sentiment <- cbind(df, select(sentiments,-text))
-
-pos <- summary_sentiment %>% 
-  arrange(desc(compound)) %>% 
-  head()
-
-for( i in rownames(pos) ) { 
-  print(pos[i, "text"]) 
-  print(pos[i, "compound"])
-}
-
-neg <- summary_sentiment %>% 
-  arrange(compound) %>% 
-  head()
-
-for( i in rownames(neg) ) { 
-  print(neg[i, "text"]) 
-  print(neg[i, "compound"])
-}
+summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
 ```
@@
 #tweet_sentiment$date <- as.Date(tweet_sentiment$created) 
+summary_sentiment <- summary_sentiment %>%
+  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
+                       ifelse(cosponsor_D_perc < 0.5,"Rep",
+                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))
 
@@
   summarise(score = mean(compound)) %>% 
-  pivot_wider(names_from = partisan, values_from = score)
+  pivot_wider(names_from = partisan, values_from = score) %>%
+  select(-c("Neutral", "NA"))
 
@@
 ggplot(daily_sentiment, aes(date, colour=partisan)) +
-  geom_point(aes(y=score),size=0.5) + geom_line(aes(y=score7))
+  geom_point(aes(y=score), size=0.5) + 
+  geom_line(aes(y=score7)) + theme_minimal()
 ```

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 ```
+
+## Creating party variable
+```{r }
+df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
+```
+
 ## Creating a corpus
@@
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-    dfm_trim(min_termfreq = 1)
+    dfm_trim(min_termfreq = 3)
 
@@
 
-dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
+dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
     dfm_trim(min_termfreq = 3)
@@
 textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
-                   color = c("blue", "red"))
+                   color = c("green","blue", "red"))
+
+```
+
+#Wordcloud congress parties 115
+
+```{r }
+
+corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
+modelpart15 <- dfm(corp_115, remove = stopwords("english"), remove_punct = TRUE, groups = corp_115$party) %>% dfm_trim(min_termfreq = 3)
+
+mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
+                   color = c("green","blue", "red"))
+mp15
+
+```
+
+#Wordcloud congress parties 116
+
+```{r }
+
+corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
+modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_punct = TRUE, groups = corp_116$party) %>% dfm_trim(min_termfreq = 3)
+
+mp16 <- textplot_wordcloud(modelpart16, comparison = TRUE, max_words = 300,
+                   color = c("green","blue", "red"))
+mp16
+
+```
+
+#Wordcloud congress parties 117
+
+```{r }
+
+corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
+modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_punct = TRUE, groups = corp_117$party) %>% dfm_trim(min_termfreq = 3)
+
+mp17 <- textplot_wordcloud(modelpart17, comparison = TRUE, max_words = 300,
+                   color = c("green","blue", "red"))
+
+mp17
 
@@
 ```{r }
-dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
+dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$session) %>%
     dfm_trim(min_termfreq = 3)

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 ```{r }
+#if two thirds of the sponsors are democrats, we consider the bill democrat-dominated
+#same for republicans
+#if there is no clear majority, they are "Both"
 df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 
-dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
+dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$party) %>%
+   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
     dfm_trim(min_termfreq = 3)
@@
 corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
-modelpart15 <- dfm(corp_115, remove = stopwords("english"), remove_punct = TRUE, groups = corp_115$party) %>% dfm_trim(min_termfreq = 3)
+modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
+   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
 
@@
 corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
-modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_punct = TRUE, groups = corp_116$party) %>% dfm_trim(min_termfreq = 3)
+modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
 
@@
 corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
-modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_punct = TRUE, groups = corp_117$party) %>% dfm_trim(min_termfreq = 3)
+modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_117$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
 

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 library(tidyr)
+
 ```
@@
 ```{r }
-dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$session) %>%
+dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
   dfm_trim(min_termfreq = 3)

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 
-ggplot(daily_sentiment, aes(date, colour=partisan)) +
-  geom_point(aes(y=score), size=0.5) + 
-  geom_line(aes(y=score7)) + theme_minimal()
+ggplot(daily_sentiment, aes(x=date, y = score, colour=partisan)) +
+  geom_point(aes(y=score), size=1) + 
+  geom_line(aes(y=score7)) + theme_minimal() + geom_smooth(method = "lm")
 ```

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

--- 2022-11-28 draft_final_assingment.Rmd
@@
 
+```{r}
+ggplot(df, aes(x = cosponsor_D_perc)) + 
+  geom_histogram(aes(y=..density..), colour="black", fill="white") +
+  geom_density(alpha=.1, fill="blue") +
+  labs(title="Density of bill cosposor party",
+       x ="Cosponsor party composition", y = "Density", 
+       caption = "Numbers represent proportion of cosponsors from Democratic party, 
+       so 0.0 represents bills that were fully Republican and 1.0 represents 
+       bills that were fully Democrat.") +
+  theme_minimal()
+```
+
 ## Creating a corpus
@@
   tokens_remove(patter = stopwords("en")) %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
+  tokens_wordstem() %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author")) %>%
   dfm()
@@
 #Do we also want to lemmatize and apply word stems??
-
 # tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
-
 # tokens_wordstem() %>%
@@
 ```{r }
-dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
-                remove_numbers = TRUE) %>%
-  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-    dfm_trim(min_termfreq = 3)
+dfmat_115 <- dfm_subset(dfmat, session == 115)
 
@@
 ```{r }
-dfmat_116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
-                remove_numbers = TRUE) %>%
-  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-    dfm_trim(min_termfreq = 1)
+dfmat_116 <- dfm_subset(dfmat, session == 116)
 
@@
 ```{r }
-dfmat_117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
-                remove_numbers = TRUE) %>%
-  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-    dfm_trim(min_termfreq = 1)
+dfmat_117 <- dfm_subset(dfmat, session == 117)
 
@@
 ```{r }
-#Need to get sponsor party data
-
-dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$party) %>%
+dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
+                     corp$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
@@
                    color = c("green","blue", "red"))
-
 ```
@@
 mp15
-
 ```
@@
                    color = c("blue", "red"))
-
 ```
@@
 ```
+## Most common words by party
+
+```{r}
+#Republicans
+dfmat_r <- dfm_subset(dfmat, party == "Republican")
+
+tfreq_r <- dfmat_r %>%
+  textstat_frequency() %>%
+  head(20)
+
+tfreq_r$feature <- factor(tfreq_r$feature, levels=tfreq_r$feature)
+
+ggplot(tfreq_r, aes(x=frequency, y=feature)) +
+geom_col() + labs(title="Feature (word) frequency for Republican Bills",
+        x ="Frequency", y = "Feature") +
+  theme_minimal() 
+```
+
+```{r}
+#Democrats
+dfmat_d <- dfm_subset(dfmat, party == "Democrat")
+
+tfreq_d <- dfmat_d %>%
+  textstat_frequency() %>%
+  head(20)
+
+tfreq_d$feature <- factor(tfreq_d$feature, levels=tfreq_d$feature)
+
+ggplot(tfreq_d, aes(x=frequency, y=feature)) +
+geom_col() + labs(title="Feature (word) frequency for Democrat Bills",
+        x ="Frequency", y = "Feature") +
+  theme_minimal() 
+```
+
+```{r}
+party_corp <- corpus_subset(corp, 
+                            party %in% c("Democrat", "Republican"))
+
+# Create a dfm grouped by party
+party_dfm <- tokens(party_corp, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
+  tokens_wordstem() %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author", "may")) %>%
+  tokens_group(groups = party) %>%
+  dfm()
+
+# Calculate keyness and determine Republican as target group
+result_keyness <- textstat_keyness(party_dfm, target = "Republican")
+
+# Plot estimated word keyness
+textplot_keyness(result_keyness) 
+```
+
 ## Most common words (by session)
@@
 ```{r}
-sims <- textstat_simil(dfm_corp, method="cosine")
+sims <- textstat_simil(dfmat, method="cosine")
 
@@
 ```{r }
-df <- df %>%
-  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
-                       ifelse(cosponsor_D_perc < 0.5,"Rep",
-                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))
+corp2 <- corpus(df$summary)
 
-corp <- corpus(df$summary)
-
-dfmat2 <- corp %>%
+dfmat2 <- corp2 %>%
   tokens(remove_punct = TRUE) %>%
@@
 
-colordict <- c( "Dem"="blue","Rep"="red", "Neutral"="yellow")
+colordict <- c( "Democrat"="blue","Republican"="red", "Both"="yellow")
 
-p <- ggplot(df, aes(x, y, fill=partisan)) + 
+ggplot(df, aes(x, y, fill=party)) + 
   geom_point(color="grey", shape=21, size=0.5) + 
   scale_fill_manual(values=colordict) +
-  theme_bw() +
-  coord_fixed()
-
-p
+  theme_bw()
 ```
@@
 ```{r}
-library(tidyr)
-#tweet_sentiment$date <- as.Date(tweet_sentiment$created) 
-summary_sentiment <- summary_sentiment %>%
-  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
-                       ifelse(cosponsor_D_perc < 0.5,"Rep",
-                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))
+summary_sentiment$party <- ifelse(summary_sentiment$cosponsor_D_perc > 0.66, "Democrat", ifelse(summary_sentiment$cosponsor_R_perc > 0.66, "Republican", "Both"))
 
 wide_sentiment <- summary_sentiment %>%
-  group_by(partisan, date) %>%
+  group_by(party, date) %>%
   summarise(score = mean(compound)) %>% 
-  pivot_wider(names_from = partisan, values_from = score) %>%
-  select(-c("Neutral", "NA"))
+  pivot_wider(names_from = party, values_from = score) %>%
+  select(-c("Both", "NA"))
 
@@
   left_join(wide_sentiment) %>% 
-  pivot_longer(cols = -date, names_to="partisan", values_to="score") %>%
-  group_by(partisan) %>% 
+  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
+  group_by(party) %>% 
   arrange(date) %>%
@@
 
-ggplot(daily_sentiment, aes(date, colour=partisan)) +
-  geom_point(aes(y=score), size=0.5) + 
-  geom_line(aes(y=score7)) + theme_minimal()
+ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
+  geom_point(aes(y=score), size=1) + 
+  geom_line(aes(y=score7)) + 
+  theme_minimal() + 
+  geom_smooth(method = "lm")
 ```
+```{r}
+summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc > 1.0, "Rep", "NA"))
+
+wide_sentiment_full <- summary_sentiment %>%
+  group_by(party, date) %>%
+  summarise(score = mean(compound)) %>% 
+  pivot_wider(names_from = party, values_from = score) %>%
+  select(-c("Both", "NA")) %>%
+  drop_na(Democrat, Republican)
+
+days_115 <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2018-12-31"),1))
+
+daily_sentiment_115 <- days_115 %>% 
+  left_join(wide_sentiment_full) %>% 
+  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
+  group_by(party) %>% 
+  arrange(date) %>%
+  mutate(score7 = data.table::frollmean(score, 7))
+
+daily_sentiment %>% head()
+
+ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party)) +
+  geom_point(aes(y=score), size=1) + 
+  geom_line(aes(y=score7)) + 
+  theme_minimal() + 
+  geom_smooth(method = "lm")
+```
+
+```{r}
+days_116 <- data.frame(date = seq(as.Date("2019-01-01"),as.Date("2020-12-31"),1))
+
+daily_sentiment_116 <- days_116 %>% 
+  left_join(wide_sentiment_full) %>% 
+  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
+  group_by(party) %>% 
+  arrange(date) %>%
+  mutate(score7 = data.table::frollmean(score, 7))
+
+daily_sentiment_116 %>% head()
+
+ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party)) +
+  geom_point(aes(y=score), size=1) + 
+  geom_line(aes(y=score7)) + 
+  theme_minimal() + 
+  geom_smooth(method = "lm")
+```
+```{r}
+days_117 <- data.frame(date = seq(as.Date("2021-01-01"),as.Date("2022-12-31"),1))
+
+daily_sentiment_117 <- days_117 %>% 
+  left_join(wide_sentiment_full) %>% 
+  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
+  group_by(party) %>% 
+  arrange(date) %>%
+  mutate(score7 = data.table::frollmean(score, 7))
+
+ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party)) +
+  geom_point(aes(y=score), size=1) + 
+  geom_line(aes(y=score7)) + 
+  theme_minimal() + 
+  geom_smooth(method = "lm")
+```

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 library(tidyr)
+library(tidymodels) 
+library(textrecipes)
 ```
@@
 
-daily_sentiment %>% head()
-
 ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
@@
 ```{r}
-summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc > 1.0, "Rep", "NA"))
+summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc == 1.0, "Rep", NA))
 
 wide_sentiment_full <- summary_sentiment %>%
-  group_by(party, date) %>%
+  drop_na(party_full) %>%
+  group_by(party_full, date) %>%
   summarise(score = mean(compound)) %>% 
-  pivot_wider(names_from = party, values_from = score) %>%
-  select(-c("Both", "NA")) %>%
-  drop_na(Democrat, Republican)
+  pivot_wider(names_from = party_full, values_from = score)
 
@@
   left_join(wide_sentiment_full) %>% 
-  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
-  group_by(party) %>% 
+  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
+  group_by(party_full) %>% 
   arrange(date) %>%
@@
 
-ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party)) +
+ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party_full)) +
   geom_point(aes(y=score), size=1) + 
@@
 
-ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party)) +
+ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party_full)) +
   geom_point(aes(y=score), size=1) + 
@@
 
-ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party)) +
+ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party_full)) +
   geom_point(aes(y=score), size=1) + 
@@
 ```
+##Some machine learning
+
+```{r}
+#Prediction model to see if can predict if bill is Republican or Democrat
+
+#Keep only bills that are over 66% Democrat or Republican
+df1 <- df %>%
+  filter(party != "Both")
+
+df1 <- df1[sample(nrow(df1)),]
+df1$env <- 0
+df1$env[df1$party == "Republican"] <- 1
+df1$env <- factor(df1$env)
+
+df_split <- initial_split(df1, prop=0.8) 
+train_data <- training(df_split) 
+test_data <- testing(df_split)
+
+rec <- recipe(env ~ summary, data = train_data) %>% 
+  step_tokenize(summary) %>% 
+  step_tokenfilter(summary, max_tokens = 1e3) %>% 
+  step_tfidf(summary)
+
+model <- svm_linear(mode="classification")
+
+wf <- workflow() %>% 
+  add_recipe(rec) %>% 
+  add_model(model)
+
+model_fit <- wf %>% 
+  fit(train_data)
+```
+
+```{r}
+test_data$prediction <- predict(model_fit, test_data)$.pred_class
+
+scorer <- metric_set( yardstick::accuracy, 
+                      yardstick::precision, 
+                      yardstick::recall, 
+                      yardstick::f_meas
+)
+
+scorer(test_data, truth=env, estimate=prediction, event_level="second")
+```
+
+```{r}
+#Prediction model to see if can predict if bill is focusing on health (as policy area)
+
+df2 <- df[sample(nrow(df)),]
+df2$env <- 0
+df2$env[df2$policy_area == "Health"] <- 1
+df2$env <- factor(df2$env)
+
+df_split <- initial_split(df2, prop=0.8) 
+train_data <- training(df_split) 
+test_data <- testing(df_split)
+
+rec <- recipe(env ~ summary, data = train_data) %>% 
+  step_tokenize(summary) %>% 
+  step_tokenfilter(summary, max_tokens = 1e3) %>% 
+  step_tfidf(summary)
+
+model <- svm_linear(mode="classification")
+
+wf <- workflow() %>% 
+  add_recipe(rec) %>% 
+  add_model(model)
+
+model_fit <- wf %>% 
+  fit(train_data)
+```
+
+```{r}
+test_data$prediction <- predict(model_fit, test_data)$.pred_class
+
+scorer <- metric_set( yardstick::accuracy, 
+                      yardstick::precision, 
+                      yardstick::recall, 
+                      yardstick::f_meas
+)
+
+scorer(test_data, truth=env, estimate=prediction, event_level="second")
+```

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
 ##Sentiments
-```{r}
-lex <- get_sentiments("afinn")
-
-text_tokens <- tidy(dfmat) %>% 
-  inner_join(lex, by=c("term" = "word"))
-
-doc_sentiments <- tidy(dfmat) %>% 
-  inner_join(lex, by=c("term" = "word")) %>% 
-  mutate(value=value*count) %>% 
-  group_by(document) %>%
-  summarise(value = sum(value))
-
-doc_sentiments
-```
 
@@
 summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
+```
+```{r}
+ggplot(summary_sentiment, aes(x = compound)) + 
+  geom_histogram(aes(y=..density..), colour="black", fill="white") +
+  geom_density(alpha=.1, fill="blue") +
+  labs(title="Density of compount sentiment scores",
+       x ="Sentiment scores", y = "Density") +
+  theme_minimal()
 ```

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
   geom_density(alpha=.1, fill="blue") +
-  labs(title="Density of compount sentiment scores",
+  labs(title="Density of compound sentiment scores",
        x ="Sentiment scores", y = "Density") +

### 2022-11-29 slides/slides.qmd
data & slides

---
title: "Congress text mining"
title-slide-attributes:
    data-background-image: /layout/background.jpg
    title-slide-style: 
subtitle: "Text as Data Assignment 3"
date: 01.12.2022
format:
    revealjs:
        code-fold: true
        code-tools: true
        theme: sky
        slide-number: true
        preview-links: auto
        footer: "[github.com/juka19/tad_assignment3](https://github.com/juka19/tad_assignment3)"
        transition: slide
        transition-speed: fast
        background-transition: fade
filters:
    - reveal-auto-agenda
    - designmode
auto-agenda:
    bullets: numbered
    heading: Agenda
auto-play-media: true
---

# Research question

# Data acquisition & preprocessing

## Overview
- Data from the 115^th^, 116^th^ and 117^th^ US congress 
- Text summaries of public laws
- Metadata
    - sponsors, cosponsors, actions, policy fields, ...

## Data acquisition

::: {.panel-tabset}

### Challenges 
- Paginated output
- Multiple API calls for each observation
- Request limit of 1000 API calls per hour

[Not knowing about bulk download options of ProRepublica... {{< fa regular face-rolling-eyes >}}]{.fragment}

### Code

```{.python }
@congress_deco(output_format='json')
def get_congress_data(query:str, *args, api_key=os.getenv('US.GOV_API')) -> dict:

        hdr = {
                # specifying requested encoding
                'Cache-Control': 'no-cache',
                'charset': 'UTF-8',
                'X-Api-Key': api_key,
                'User-Agent': random.choice(['Mozilla/5.0', 'Chrome 104.0.0.0', 
                                                'Chrome 52.0.2762.73', 'Chrome 55.0.2919.83'])
                }

        BASE_URL = 'https://api.congress.gov/v3/'

        query_url = BASE_URL + query

        if args: # concatenate variable arguments to url
                query_url += '&' + '&'.join(args)

        return (query_url, hdr)
```

:::
## Data acquisition 3

```{.python }
@congress_deco(output_format='html')
def get_bill_text(query:str) -> str:

        hdr = {
                # specifying requested encoding
                'Cache-Control': 'no-cache',
                'charset': 'UTF-8',
                'User-Agent': random.choice(['Mozilla/5.0', 'Chrome 104.0.0.0', 
                                                'Chrome 52.0.2762.73', 'Chrome 55.0.2919.83'])
                }

        return (query, hdr)
```

## Data

```{.python}
import plotly.ex

```

## Preprocessing

# Methods

# Results

# Discussion

# Conclusion

### 2022-11-29 multi_thread_script.py

@@ -30,11 +30,17 @@ def congress_deco(output_format='json') -> object:
                                         
                                         output = json.loads(output)
                                         
+                                        return output
+                                        
                                 if output_format == 'html':
                                         
                                         output = response.read()
+                                        
+                                        return output
+                        
+                        except urllib.request.HTTPError:
                                 
-                                return output
+                                time.sleep(60*60)
                         
                         except Exception as e:
                                 
@@ -93,32 +99,33 @@ def loop_function(api_key, url):
             
             bill_number = metadata['bill']['number']
             policy_area = metadata['bill']['policyArea']['name']
-            if 'cosponsors' in metadata['bill'].keys():
-                    cosponsors = get_congress_data(get_root_url(metadata['bill']['cosponsors']['url']) + "?limit=250", api_key=api_key)
-                    cosponsor_D = 0
-                    cosponsor_R = 0
-                    cosponsor_l = []
-                    for cosponsor in cosponsors['cosponsors']:
-                            cosponsor_party = cosponsor['party']
-                            if cosponsor_party == "D":
-                                    cosponsor_D += 1 
-                            if cosponsor_party == "R":
-                                    cosponsor_R += 1
-                            cosponsor_name = cosponsor['firstName'] + ' ' + cosponsor['lastName']
-                            cosponsor_party = cosponsor['party']
-                            cosponsor_l.append({'cosponsor_name': cosponsor_name, 'cosponsor_party': cosponsor_party, 'number': bill_number})
-                    #number = int(output_l[0]['metadata']['bill']['number'])
-                    if (cosponsor_D + cosponsor_R)!= 0:
-                            cosponsor_D_perc = cosponsor_D/(cosponsor_D + cosponsor_R)
-                            cosponsor_R_perc = cosponsor_R/(cosponsor_D + cosponsor_R)
-            else:
-                    cosponsor_D_perc = 0
-                    cosponsor_R_perc = 0
-                    cosponsor_l = []
+        #     if 'cosponsors' in metadata['bill'].keys():
[…]

### 2022-11-29 slides/plots.py

@@ -1,0 +1,46 @@
+import plotly.express as px
+import pandas as pd
+
+df = pd.read_csv("data\\data_28_11_sponsors.csv")
+df['date'] = pd.to_datetime(df.date)
+
+spons_df = pd.read_csv('data\\cosponsors_sponsors.csv')
+
+grp_dat =(spons_df
+ .groupby(['number', 'cosponsor_party'])
+ .agg({'cosponsor_name': 'count'})
+ .reset_index()
+)
+grp_dat['perc'] = grp_dat.groupby('number')['cosponsor_name'].apply(lambda x: x*100/x.sum())
+
+test = grp_dat.merge(df, left_on='number', right_on='bill.number')
+test = test[test['cosponsor_party'] == 'D'].groupby(['session', 'policy_area']).agg({'perc': 'mean'}).reset_index()
+
+a = px.colors.qualitative.T10[2]
+b = px.colors.qualitative.T10[-1]
+c = px.colors.qualitative.T10[0]
+
+fig = px.line_polar(
+    test, 
+    r='perc',
+    theta='policy_area',
+    color='session',
+    line_close=True,
+    color_discrete_sequence=[a,b,c],
+    # color_discrete_sequence=px.colors.sequential.Plasma_r,
+    template='plotly_dark',
+    custom_data=['perc', 'policy_area', 'session']
+              )
+
+fig.update_layout(showlegend=False)
+fig.update_layout(font_size=6, font_color='#000000')
+fig.update_traces(hovertemplate='Session: %{customdata[2]} <br>Policy Area: %{customdata[1]} <br>Democratic Cosponsors: %{customdata[0]:.0%}')
+fig.update_layout(
+    paper_bgcolor='rgba(0,0,0,0)',
+    plot_bgcolor='rgba(0,0,0,0)'
+)
+fig.update_polars('rgba(0,0,0,0)')
+fig.show()
+
+
+

### 2022-11-29 slides/slides.qmd
update

@@
 :::
-## Data acquisition 3
-
-```{.python }
-@congress_deco(output_format='html')
-def get_bill_text(query:str) -> str:
-
-        hdr = {
-                # specifying requested encoding
-                'Cache-Control': 'no-cache',
-                'charset': 'UTF-8',
-                'User-Agent': random.choice(['Mozilla/5.0', 'Chrome 104.0.0.0', 
-                                                'Chrome 52.0.2762.73', 'Chrome 55.0.2919.83'])
-                }
-
-        return (query, hdr)
-```
 
@@
 ```{.python}
-import plotly.ex
+import plotly.express as px
+import pandas as pd
+
+df = pd.read_csv("data\\data_28_11_sponsors.csv")
 

### 2022-11-29 slides/slides.qmd
push slides2

@@
 auto-play-media: true
+jupyter: python3
 ---
@@
 
-```{.python}
-import plotly.express as px
-import pandas as pd
+## Share of Cosponsors across Policy fields
 
-df = pd.read_csv("data\\data_28_11_sponsors.csv")
-
+```{python, fullscreen=true}
+import plotly.io as pio
+fig = pio.read_json('plots\\polar_line_plot')
+fig.show()
 ```

### 2022-11-29 slides/plots.py

@@ -13,34 +13,38 @@ grp_dat =(spons_df
 )
 grp_dat['perc'] = grp_dat.groupby('number')['cosponsor_name'].apply(lambda x: x*100/x.sum())
 
-test = grp_dat.merge(df, left_on='number', right_on='bill.number')
-test = test[test['cosponsor_party'] == 'D'].groupby(['session', 'policy_area']).agg({'perc': 'mean'}).reset_index()
+df_final = grp_dat.merge(df, left_on='number', right_on='bill.number')
+
+df_final = df_final[df_final['cosponsor_party'] == 'D'].groupby(['session', 'policy_area']).agg({'perc': 'mean'}).reset_index()
 
 a = px.colors.qualitative.T10[2]
 b = px.colors.qualitative.T10[-1]
 c = px.colors.qualitative.T10[0]
 
+df_final.sort_values(by=['session', 'policy_area'], inplace=True)
+df_final = df_final[df_final['policy_area'] != 'Housing and Community Development']
+plot_df = df_final.round(1)
 fig = px.line_polar(
-    test, 
+    plot_df, 
     r='perc',
     theta='policy_area',
     color='session',
     line_close=True,
     color_discrete_sequence=[a,b,c],
     # color_discrete_sequence=px.colors.sequential.Plasma_r,
-    template='plotly_dark',
-    custom_data=['perc', 'policy_area', 'session']
+    template='plotly_dark'
               )
 
 fig.update_layout(showlegend=False)
-fig.update_layout(font_size=6, font_color='#000000')
-fig.update_traces(hovertemplate='Session: %{customdata[2]} <br>Policy Area: %{customdata[1]} <br>Democratic Cosponsors: %{customdata[0]:.0%}')
-fig.update_layout(
-    paper_bgcolor='rgba(0,0,0,0)',
-    plot_bgcolor='rgba(0,0,0,0)'
-)
-fig.update_polars('rgba(0,0,0,0)')
+fig.update_layout(font_size=6)
+fig.update_traces(hovertemplate='Policy Area: %{theta} <br>Democratic Cosponsors: %{r}')
+# fig.update_layout(
+#     paper_bgcolor='rgba(0,0,0,0)',
+#     plot_bgcolor='rgba(0,0,0,0)'
+# )
 fig.show()
 
+
+fig.to_plotly_json('')
 
 

### 2022-11-29 slides/slides.qmd
Update slides.qmd

@@
 
+-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
+
+    -   in 2016, both chambers were hold by Republicans
+
+    -   in 2018, the Democrats gained a majority in Congress
+
+    -   in 2020 the Democrats gained Congress and Senate
+
+-   While one might expect that the post 2016 and 2020 congresses will vary in their topics and policies.
+However, it is interesting to also focus on the period between 2018 and 2020: When both chambers had different majorities and needed to cooperate.
+
+-   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
+
 # Data acquisition & preprocessing
@@
 ## Overview
+
 -   Data from the 115^th^, 116^th^ and 117^th^ US congress
@@
 
-::: {.panel-tabset}
+::: panel-tabset
+### Challenges
 
-### Challenges 
 -   Paginated output
@@
 
-```{.python }
+``` python
 @congress_deco(output_format='json')
@@
 ```
-
 :::

### 2022-11-29 slides/slides.qmd
Update slides.qmd

@@
 
+::: columns
+::: {.column width="80%"}
 -   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
@@
 -   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
+:::
+
+::: {.column width="20%"}
+![](https://www.politico.com/dims4/default/0ba7efa/2147483647/strip/true/crop/1160x773+0+0/resize/1290x860!/quality/90/?url=https%253A%252F%252Fstatic.politico.com%252Fa3%252F2c%252Ffbd235e445b4a96e0373e3060e3c%252Fgettyimages-1294351903-1.jpg){width="300"}
+:::
+:::
 

### 2022-11-30 draft_final_assingment.Rmd
Nov30draft

@@
 library(textrecipes)
+library(plotly)
 ```
@@
 #if there is no clear majority, they are "Both"
+
 df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
@@
 
+##Dimensionality plotting
+
 ```{r }
@@
 
-ggplot(df, aes(x, y, fill=party)) + 
+p <- ggplot(df, aes(x, y, fill=party)) + 
   geom_point(color="grey", shape=21, size=0.5) + 
@@
   theme_bw()
+
+p
+ggplotly(p)
+```
+
+```{r }
+df1 <- df %>%
+  mutate(party_full = ifelse(cosponsor_D_perc == 1.0, "Dem",
+                             ifelse(cosponsor_R_perc == 1.0, "Rep", NA))) %>%
+  drop_na(party_full)
+
+corp3 <- corpus(df1$summary)
+
+dfmat3 <- corp3 %>%
+  tokens(remove_punct = TRUE) %>%
+  tokens_remove(patter = stopwords("en")) %>%
+  dfm() %>%
+  dfm_trim(min_termfreq = 5)
+
+embeddings2 <- umap(as.matrix(dfmat3))
+
+df1$x <- embeddings2[,1]
+df1$y <- embeddings2[,2]
+
+colordict2 <- c( "Democrat"="blue","Republican"="red")
+
+j <- ggplot(df1, aes(x, y, fill=party)) + 
+  geom_point(color="grey", shape=21, size=0.5) + 
+  scale_fill_manual(values=colordict2) +
+  theme_bw()
+
+j
+ggplotly(j)
 ```

### 2022-11-30 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

@@
   tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program")) %>%
   dfm()

### 2022-11-30 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

--- 2022-11-30 draft_final_assingment.Rmd
@@
   tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl")) %>%
   dfm()

### 2022-11-30 draft_final_assingment.Rmd
Update

--- 2022-11-30 draft_final_assingment.Rmd
@@
   tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
   dfm()

### 2022-11-30 aw_final_assignment.Rmd
Add files via upload

---
title: "aw_final_assignment"
author: "Andrew Wells"
date: "11/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(ggplot2)
library(gridExtra) 
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

```{r, warning=FALSE}
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")

df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```

## Density of bill cosponsors
```{r, warning=FALSE}

p <- ggplot(df, aes(x = cosponsor_D_perc)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of bill cosposor party",
       x ="Cosponsor party composition", y = "Density", 
       caption = "Numbers represent proportion of cosponsors from Democratic party, 
       so 0.0 represents bills that were fully Republican and 1.0 represents 
       bills that were fully Democrat.") +
  theme_minimal()

ggplotly(p)
```

```{r, warning=FALSE}
p1 <- df %>%
  filter(party == "Republican") %>%
  ggplot(aes(factor(policy_area))) +
  geom_bar(stat="count", position = "dodge") + 
  scale_fill_brewer(palette = "Set1") + 
    labs(title="Policy areas addressed by Republican bills",
       x ="Count", y = "Policy areas") +
  theme_minimal() +
  coord_flip()

p2 <- df %>%
  filter(party == "Democrat") %>%
  ggplot(aes(factor(policy_area))) +
  geom_bar(stat="count", position = "dodge") + 
  scale_fill_brewer(palette = "Set1") + 
    labs(title="Policy areas addressed by Democrat bills",
       x ="Count", y = "Policy areas") +
  theme_minimal() +
  coord_flip()

grid.arrange(p1, p2, nrow = 1)
```

##Dimensionality plotting

```{r }
corp2 <- corpus(df$summary)

dfmat2 <- corp2 %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm() %>%
  dfm_trim(min_termfreq = 5)

embeddings <- umap(as.matrix(dfmat2))

df$x <- embeddings[,1]
df$y <- embeddings[,2]

colordict <- c( "Democrat"="blue","Republican"="red", "Both"="yellow")

p3 <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw()

ggplotly(p3)
```

##Sentiment analysis

```{r}
summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")

summary_sentiment$party <- ifelse(summary_sentiment$cosponsor_D_perc > 0.66, "Democrat", ifelse(summary_sentiment$cosponsor_R_perc > 0.66, "Republican", "Both"))

wide_sentiment <- summary_sentiment %>%
  group_by(party, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = party, values_from = score) %>%
  select(-c("Both", "NA"))

days <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2022-12-31"),1))

daily_sentiment <- days %>% 
  left_join(wide_sentiment) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score")

p4 <- ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  theme_minimal() + 
  geom_smooth(method = "loess", se = FALSE)

ggplotly(p4)
```

### 2022-11-30 draft_final_assingment.Rmd
push rmd

--- 2022-11-30 draft_final_assingment.Rmd
@@
 date: "11/18/2022"
-output: html_document
+output: 
+  html_document:
+    toc: TRUE
+    theme: cosmo
+    toc_float: TRUE
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r }
 library(tidyverse)
@@
 
-##Creatung a dfm from the corpus
+## Creatung a dfm from the corpus
 ```{r }
@@
   tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
   dfm()
@@
 
-##Most common words in the corpus
+## Most common words in the corpus
 ```{r }
@@
 ```
-#Wordcloud congress 115
 
-```{r }
+# Wordclouds
+
+## Wordcloud congress 115
+
+```{r, wa }
 dfmat_115 <- dfm_subset(dfmat, session == 115)
@@
 
-#Wordcloud congress 116
+## Wordcloud congress 116
 
-```{r }
+```{r, wa }
 dfmat_116 <- dfm_subset(dfmat, session == 116)
@@
 ```
-#Wordcloud congress 117
+## Wordcloud congress 117
 
-```{r }
+```{r, wa }
 dfmat_117 <- dfm_subset(dfmat, session == 117)
@@
 
-#Wordcloud comparing Democrats and Republicans
-```{r }
+## Wordcloud comparing Democrats and Republicans
+```{r, wa }
 dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
@@
 
-#Wordcloud congress parties 115
+## Wordcloud congress parties 115
 
-```{r }
+```{r, wa }
 
@@
 
-#Wordcloud congress parties 116
+## Wordcloud congress parties 116
 
-```{r }
+```{r, wa }
 
@@
 
-#Wordcloud congress parties 117
+## Wordcloud congress parties 117
 
-```{r }
+```{r, wa }
 
@@
 
-#Wordcloud comparing Congresses
-```{r }
+## Wordcloud comparing Congresses
+```{r, wa }
 dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
@@
 ## Most common words (overall)
-```{r}
+```{r, warning=FALSE}
 #Overall most common words
@@
 
-```{r}
+```{r, warning=FALSE}
 #Republicans
@@
 
-```{r}
+```{r, warning=FALSE}
 #Democrats
@@
 
-```{r}
+```{r, warning=FALSE}
 party_corp <- corpus_subset(corp, 
@@
 
-```{r }
+```{r, warning=FALSE}
 # Most common words by Congressional session 115
@@
 
-```{r }
+```{r, warning=FALSE}
 # Most common words by Congressional session 116
@@
 
-```{r}
+```{r, warning=FALSE}
 # Most common words by Congressional session 117
@@
 
-##Comparing subgroups
-```{r}
+## Comparing subgroups
+```{r, warning=FALSE}
 df <- df %>%
@@
 ```{r}
-sims <- textstat_simil(dfmat, method="cosine")
-
-sim_df <- as.data.frame(sims, upper = TRUE)
-
-sim_df
+# sims <- textstat_simil(dfmat, method="cosine")
+# 
+# sim_df <- as.data.frame(sims, upper = TRUE)
+# 
+# sim_df
 ```
 
-##Dimensionality plotting
+## Dimensionality plotting
 
@@
 
-##Topic modeling
+## Topic modeling
 
@@
 
-##Sentiments
+## Sentiments
 
@@
 ```
-##Some machine learning
+## Some machine learning
 

### 2022-11-30 draft_final_assingment.Rmd
push rmd

@@
 
-```{r setup, include=FALSE}
+```{r setup, warning=FALSE, include=FALSE, message=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 library(plotly)
+library(reticulate)
+use_python("tad_venv3\\Scripts\\python.exe")
 ```
@@
 
-```{r, wa }
+```{r}
 dfmat_115 <- dfm_subset(dfmat, session == 115)
@@
 
-```{r, wa }
+```{r}
 dfmat_116 <- dfm_subset(dfmat, session == 116)
@@
 
-```{r, wa }
+```{r}
 dfmat_117 <- dfm_subset(dfmat, session == 117)
@@
 ## Wordcloud comparing Democrats and Republicans
-```{r, wa }
+```{r}
 dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
@@
 
-```{r, wa }
+```{r}
 
@@
 ## Wordcloud comparing Congresses
-```{r, wa }
+```{r}
 dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
@@
 ## Most common words (overall)
-```{r, warning=FALSE}
+```{r}
 #Overall most common words
@@
 
-```{r, warning=FALSE}
+```{r}
 #Republicans
@@
 
-```{r, warning=FALSE}
+```{r}
 #Democrats
@@
 
-```{r, warning=FALSE}
+```{r}
 party_corp <- corpus_subset(corp, 
@@
 
-```{r, warning=FALSE}
+```{r}
 # Most common words by Congressional session 115
@@
 
-```{r, warning=FALSE}
+```{r}
 # Most common words by Congressional session 116
@@
 
-```{r, warning=FALSE}
+```{r}
 # Most common words by Congressional session 117
@@
 ## Comparing subgroups
-```{r, warning=FALSE}
+```{r}
 df <- df %>%
@@
   geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
+```
+
+```{python}
+import plotly.io as pio
+fig = pio.read_json('slides\\plots\\polar_line_plot')
+fig.show()
 ```

### 2022-11-30 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

--- 2022-11-30 draft_final_assingment.Rmd
@@
 ---
+# Research question
+
+-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
+
+    -   in 2016, both chambers were hold by Republicans
+
+    -   in 2018, the Democrats gained a majority in Congress
+
+    -   in 2020 the Democrats gained Congress and Senate
+
+-   While one might expect that the post 2016 and 2020 congresses will vary in their topics and policies.
+However, it is interesting to also focus on the period between 2018 and 2020: When both chambers had different majorities and needed to cooperate.
+
+-   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
+
+![](https://www.politico.com/dims4/default/0ba7efa/2147483647/strip/true/crop/1160x773+0+0/resize/1290x860!/quality/90/?url=https%253A%252F%252Fstatic.politico.com%252Fa3%252F2c%252Ffbd235e445b4a96e0373e3060e3c%252Fgettyimages-1294351903-1.jpg){width="400"}
 
@@
 ## Creating party variable
+
 ```{r }
@@
 ## Creating a corpus
+
 ```{r }
@@
 ## Creatung a dfm from the corpus
+
 ```{r }
@@
 ## Most common words in the corpus
+
 ```{r }
@@
 # Wordclouds
+
+## Most common words in all congresses
+
+```{r, warning = FALSE}
+
+dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
+
+textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
+                   color = c("blue", "red"))
+
+#Wordcloud congress 115
+```
+
+## Comparing the 115th and 116th congress
+
+```{r, warning = FALSE}
+
+dfmat_115 <- dfm_subset(dfmat, session == 115)
+corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
+modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
+   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
+
+mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
+                   color = c("green","blue", "red"))
+
+corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
+modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+  dfm_trim(min_termfreq = 3)
+
+mp16 <- textplot_wordcloud(modelpart16, comparison = TRUE, max_words = 300,
+                   color = c("green","blue", "red"))
+```
 
@@
 ```
+
 ## Wordcloud congress 117
@@
 ## Wordcloud comparing Democrats and Republicans
+
 ```{r, wa }
@@
 ## Wordcloud comparing Congresses
+
 ```{r, wa }
@@
 ## Most common words (overall)
+
 ```{r, warning=FALSE}
@@
 ```
+
 ## Most common words by party
@@
 ## Comparing subgroups
+
 ```{r, warning=FALSE}
@@
 ```
+
 ## Some machine learning

### 2022-11-30 draft_final_assingment.Rmd
Summary_final_assignment.Rmd

@@
 ---
-# Research question
-
--   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
-
-    -   in 2016, both chambers were hold by Republicans
-
-    -   in 2018, the Democrats gained a majority in Congress
-
-    -   in 2020 the Democrats gained Congress and Senate
-
--   While one might expect that the post 2016 and 2020 congresses will vary in their topics and policies.
-However, it is interesting to also focus on the period between 2018 and 2020: When both chambers had different majorities and needed to cooperate.
-
--   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
-
-![](https://www.politico.com/dims4/default/0ba7efa/2147483647/strip/true/crop/1160x773+0+0/resize/1290x860!/quality/90/?url=https%253A%252F%252Fstatic.politico.com%252Fa3%252F2c%252Ffbd235e445b4a96e0373e3060e3c%252Fgettyimages-1294351903-1.jpg){width="400"}
 
@@
 
+# Research question
+
+-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
+
+    -   in 2016, both chambers were hold by Republicans
+
+    -   in 2018, the Democrats gained a majority in Congress
+
+    -   in 2020 the Democrats gained Congress and Senate
+
+-   While one might expect that the post 2016 and 2020 congresses will vary in their policies.
+However, it is interesting to also focus on the period between 2018 and 2020: When both chambers had different majorities and needed to cooperate.
+
+-   We will focus on the question on whether and how the different majorities had an impact on the policies that have been passed by Congress.
+
+![](https://www.politico.com/dims4/default/0ba7efa/2147483647/strip/true/crop/1160x773+0+0/resize/1290x860!/quality/90/?url=https%253A%252F%252Fstatic.politico.com%252Fa3%252F2c%252Ffbd235e445b4a96e0373e3060e3c%252Fgettyimages-1294351903-1.jpg){width="400"}
+
+## Scraping and cleaning the data
+
+We scraped our data from: https://data.gov/developers/apis/index.html
+
 ```{r }
 df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
+head(df, 5)
 ```
@@
 
+## Summary statistics
+
+## Density of cosponsors
 ```{r}
@@
 ## Creatung a dfm from the corpus
-
 ```{r }
@@
 
-#Do we also want to lemmatize and apply word stems??
-# tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
-# tokens_wordstem() %>%
-```
-
-## Most common words in the corpus
-
-```{r }
-dfmat %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
 ```
@@
                    color = c("green","blue", "red"))
-```
-
-## Wordcloud congress 115
-
-```{r, wa }
-dfmat_115 <- dfm_subset(dfmat, session == 115)
-
-textplot_wordcloud(dfmat_115, max_words = 300)
-```
-
-## Wordcloud congress 116
-
-```{r, wa }
-dfmat_116 <- dfm_subset(dfmat, session == 116)
-
-textplot_wordcloud(dfmat_116, max_words = 300)
-```
-
-## Wordcloud congress 117
-
-```{r, wa }
-dfmat_117 <- dfm_subset(dfmat, session == 117)
-
-textplot_wordcloud(dfmat_117, max_words = 300)
 ```
@@
 
-```
-
-## Wordcloud congress parties 117
-
-```{r, wa }
-
-corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
-modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_117$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm_trim(min_termfreq = 3)
-
-mp17 <- textplot_wordcloud(modelpart17, comparison = TRUE, max_words = 300,
-                   color = c("green","blue", "red"))
-
-mp17
-
-```
-
-## Wordcloud comparing Congresses
-
-```{r, wa }
-dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm_trim(min_termfreq = 3)
-
-textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
-                   color = c("blue", "red"))
-```
-
-## Most common words (overall)
-
-```{r, warning=FALSE}
-#Overall most common words
-
-tfreq <- dfmat %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq$feature <- factor(tfreq$feature, levels=tfreq$feature)
-
-ggplot(tfreq, aes(x=frequency, y=feature)) +
-geom_col() + labs(title="Feature (word) frequency",
-        x ="Frequency", y = "Feature") +
-  theme_minimal() 
-```
-
-## Most common words by party
-
-```{r, warning=FALSE}
-#Republicans
-dfmat_r <- dfm_subset(dfmat, party == "Republican")
-
-tfreq_r <- dfmat_r %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq_r$feature <- factor(tfreq_r$feature, levels=tfreq_r$feature)
-
-ggplot(tfreq_r, aes(x=frequency, y=feature)) +
-geom_col() + labs(title="Feature (word) frequency for Republican Bills",
-        x ="Frequency", y = "Feature") +
-  theme_minimal() 
-```
-
-```{r, warning=FALSE}
-#Democrats
-dfmat_d <- dfm_subset(dfmat, party == "Democrat")
-
-tfreq_d <- dfmat_d %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq_d$feature <- factor(tfreq_d$feature, levels=tfreq_d$feature)
-
-ggplot(tfreq_d, aes(x=frequency, y=feature)) +
-geom_col() + labs(title="Feature (word) frequency for Democrat Bills",
-        x ="Frequency", y = "Feature") +
-  theme_minimal() 
-```
-
-```{r, warning=FALSE}
-party_corp <- corpus_subset(corp, 
-                            party %in% c("Democrat", "Republican"))
-
-# Create a dfm grouped by party
-party_dfm <- tokens(party_corp, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
-  tokens_remove(patter = stopwords("en")) %>%
-  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
-  tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author", "may")) %>%
-  tokens_group(groups = party) %>%
-  dfm()
-
-# Calculate keyness and determine Republican as target group
-result_keyness <- textstat_keyness(party_dfm, target = "Republican")
-
-# Plot estimated word keyness
-textplot_keyness(result_keyness) 
-```
-
-## Most common words (by session)
-
-```{r, warning=FALSE}
-# Most common words by Congressional session 115
-tfreq_115 <- dfmat_115 %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq_115$feature <- factor(tfreq_115$feature, levels=tfreq_115$feature)
-
-ggplot(tfreq_115, aes(x=frequency, y=feature)) +
-  geom_col() + labs(title="Feature (word) frequency for 115 session (2017 - 2018)",
-        x ="Frequency", y = "Feature") +
-  theme_minimal()
-```
-
-```{r, warning=FALSE}
-# Most common words by Congressional session 116
-tfreq_116 <- dfmat_116 %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature)
-
-ggplot(tfreq_116, aes(x=frequency, y=feature)) +
-  geom_col() + labs(title="Feature (word) frequency for 116 session (2019 - 2020)",
-        x ="Frequency", y = "Feature") +
-  theme_minimal()
-```
-
-```{r, warning=FALSE}
-# Most common words by Congressional session 117
-tfreq_117 <- dfmat_117 %>%
-  textstat_frequency() %>%
-  head(20)
-
-tfreq_117$feature <- factor(tfreq_117$feature, levels=tfreq_117$feature)
-
-ggplot(tfreq_117, aes(x=frequency, y=feature)) +
-  geom_col() + labs(title="Feature (word) frequency for 117 session (2021 - 2022)",
-        x ="Frequency", y = "Feature") +
-  theme_minimal()
-```
-
-## Comparing subgroups
-
-```{r, warning=FALSE}
-df <- df %>%
-  mutate(session_written = ifelse(session == 115, "session_115", 
-                             ifelse(session == 116, "session_116",
-                             ifelse(session == 117, "session_117", NA))))
-
-ytfreq <- dfmat %>% 
-  textstat_frequency(groups = df$session_written) %>%
-  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)
-```
-
-```{r}
-#Comparing sessions 115 and 116
-
-#Plot #1: differences in frequency by session
-ggplot(ytfreq, aes(x= session_116, y= session_115)) + 
-  geom_point() + theme_minimal()
-
-#Plot #2: coloring changes by session
-ytfreq$change_115_116 <- log(ytfreq$session_116 / ytfreq$session_115)
-max_change <- max(abs(ytfreq$change_115_116), na.rm=TRUE)
-
-ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
-  geom_point(color="grey", shape=21) +
-  scale_fill_gradientn(
-    colors = c("#4575b4","white","#d73027"),
-    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
-theme_bw()
-
-#Plot 3: labeling words with biggest change
-labels <- ytfreq %>% 
-  rowwise() %>% 
-  mutate(max_value = max(session_116, session_115)) %>% 
-  filter((abs(change_115_116)>0.4 & max_value>2.5) )
-
-ggplot(ytfreq, aes(x=session_116, y=session_115, fill=change_115_116)) + 
-  geom_point(color="grey", shape=21) +
-  scale_fill_gradientn(
-    colors = c("#4575b4","white","#d73027"),
-    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
-  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
-```
-
-```{r}
-#Comparing sessions 116 and 117
-ggplot(ytfreq, aes(x= session_117, y= session_116)) + 
-  geom_point() + theme_minimal()
-
-#Plot #2: coloring changes by session
-ytfreq$change_116_117 <- log(ytfreq$session_117 / ytfreq$session_116)
-max_change <- max(abs(ytfreq$change_116_117), na.rm=TRUE)
-
-ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
-  geom_point(color="grey", shape=21) +
-  scale_fill_gradientn(
-    colors = c("#4575b4","white","#d73027"),
-    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change))+
-theme_bw()
-
-#Plot 3: labeling words with biggest change
-labels <- ytfreq %>% 
-  rowwise() %>% 
-  mutate(max_value = max(session_117, session_116)) %>% 
-  filter((abs(change_116_117)>0.4 & max_value>2.5) )
-
-ggplot(ytfreq, aes(x=session_117, y=session_116, fill=change_116_117)) + 
-  geom_point(color="grey", shape=21) +
-  scale_fill_gradientn(
-    colors = c("#4575b4","white","#d73027"),
-    values = scales::rescale(c(max_change*-1,0,max_change)), limits = c(max_change*-1,max_change)) + theme_bw() +
-  geom_label_repel(data=labels, aes(label=feature), min.segment.length = 0)
-```
-
-```{r}
-# sims <- textstat_simil(dfmat, method="cosine")
-# 
-# sim_df <- as.data.frame(sims, upper = TRUE)
-# 
-# sim_df
 ```
@@
 
-## Topic modeling
+##Sentiment analysis
 
-```{r }
-#Topics for session 115 (2017 - 2018)
-
-lda_115 <- LDA(dfmat_115, 5)
-
-topic_words_115 <- tidy(lda_115, matrix="beta") %>% 
-  group_by(topic) %>%
-  slice_max(beta, n = 10) %>%
-  ungroup() %>%
-  arrange(topic, -beta)
-
-topic_words_115
-
-topic_words_115 %>%
-  mutate(term = reorder_within(term, beta, topic)) %>% 
-  ggplot(aes(beta, term, fill = factor(topic))) + 
-  geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
-```
-
-```{r }
-#Topics for session 116 (2019 - 2020)
-
-lda_116 <- LDA(dfmat_116, 5)
-
-topic_words_116 <- tidy(lda_116, matrix="beta") %>% 
-  group_by(topic) %>%
-  slice_max(beta, n = 10) %>%
-  ungroup() %>%
-  arrange(topic, -beta)
-
-topic_words_116
-
-topic_words_116 %>%
-  mutate(term = reorder_within(term, beta, topic)) %>% 
-  ggplot(aes(beta, term, fill = factor(topic))) + 
-  geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
-```
-
-```{r }
-#Topics for session 117 (2021 - 2022)
-raw.sum = apply(dfmat_117,1,FUN=sum) #Removing non-0 rows from dfmat
-dfmat_117 = dfmat_117[raw.sum != 0, ]
-
-lda_117 <- LDA(dfmat_117, 5)
-
-topic_words_117 <- tidy(lda_117, matrix="beta") %>% 
-  group_by(topic) %>%
-  slice_max(beta, n = 10) %>%
-  ungroup() %>%
-  arrange(topic, -beta)
-
-topic_words_117
-
-topic_words_117 %>%
-  mutate(term = reorder_within(term, beta, topic)) %>% 
-  ggplot(aes(beta, term, fill = factor(topic))) + 
-  geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
-```
-
-## Sentiments
-
-```{r}
-#Loading df with VADER compount scores
-
+```{r, warning = FALSE}
 summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
-```
-
-```{r}
-ggplot(summary_sentiment, aes(x = compound)) + 
-  geom_histogram(aes(y=..density..), colour="black", fill="white") +
-  geom_density(alpha=.1, fill="blue") +
-  labs(title="Density of compound sentiment scores",
-       x ="Sentiment scores", y = "Density") +
-  theme_minimal()
-```
-
-```{r}
 summary_sentiment$party <- ifelse(summary_sentiment$cosponsor_D_perc > 0.66, "Democrat", ifelse(summary_sentiment$cosponsor_R_perc > 0.66, "Republican", "Both"))
@@
   select(-c("Both", "NA"))
-
 days <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2022-12-31"),1))
-
 daily_sentiment <- days %>% 
   left_join(wide_sentiment) %>% 
-  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
-  group_by(party) %>% 
-  arrange(date) %>%
-  mutate(score7 = data.table::frollmean(score, 7))
-
-ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
+  pivot_longer(cols = -date, names_to="party", values_to="score")
+p4 <- ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
   geom_point(aes(y=score), size=1) + 
-  geom_line(aes(y=score7)) + 
   theme_minimal() + 
-  geom_smooth(method = "lm")
+  geom_smooth(method = "loess", se = FALSE)+
+  scale_color_manual(values = c("blue","red"))
+ggplotly(p4)
 ```
 
-```{r}
-summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc == 1.0, "Rep", NA))
+## Topic modeling
 
-wide_sentiment_full <- summary_sentiment %>%
-  drop_na(party_full) %>%
-  group_by(party_full, date) %>%
-  summarise(score = mean(compound)) %>% 
-  pivot_wider(names_from = party_full, values_from = score)
-
-days_115 <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2018-12-31"),1))
-
-daily_sentiment_115 <- days_115 %>% 
-  left_join(wide_sentiment_full) %>% 
-  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
-  group_by(party_full) %>% 
-  arrange(date) %>%
-  mutate(score7 = data.table::frollmean(score, 7))
-
-daily_sentiment %>% head()
-
-ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party_full)) +
-  geom_point(aes(y=score), size=1) + 
-  geom_line(aes(y=score7)) + 
-  theme_minimal() + 
-  geom_smooth(method = "lm")
-```
-
-```{r}
-days_116 <- data.frame(date = seq(as.Date("2019-01-01"),as.Date("2020-12-31"),1))
-
-daily_sentiment_116 <- days_116 %>% 
-  left_join(wide_sentiment_full) %>% 
-  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
-  group_by(party_full) %>% 
-  arrange(date) %>%
-  mutate(score7 = data.table::frollmean(score, 7))
-
-daily_sentiment_116 %>% head()
-
-ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party_full)) +
-  geom_point(aes(y=score), size=1) + 
-  geom_line(aes(y=score7)) + 
-  theme_minimal() + 
-  geom_smooth(method = "lm")
-```
-
-```{r}
-days_117 <- data.frame(date = seq(as.Date("2021-01-01"),as.Date("2022-12-31"),1))
-
-daily_sentiment_117 <- days_117 %>% 
-  left_join(wide_sentiment_full) %>% 
-  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
-  group_by(party_full) %>% 
-  arrange(date) %>%
-  mutate(score7 = data.table::frollmean(score, 7))
-
-ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party_full)) +
-  geom_point(aes(y=score), size=1) + 
-  geom_line(aes(y=score7)) + 
-  theme_minimal() + 
-  geom_smooth(method = "lm")
-```
-
-## Some machine learning
-
-```{r}
-#Prediction model to see if can predict if bill is Republican or Democrat
-
-#Keep only bills that are over 66% Democrat or Republican
-df1 <- df %>%
-  filter(party != "Both")
-
-df1 <- df1[sample(nrow(df1)),]
-df1$env <- 0
-df1$env[df1$party == "Republican"] <- 1
-df1$env <- factor(df1$env)
-
-df_split <- initial_split(df1, prop=0.8) 
-train_data <- training(df_split) 
-test_data <- testing(df_split)
-
-rec <- recipe(env ~ summary, data = train_data) %>% 
-  step_tokenize(summary) %>% 
-  step_tokenfilter(summary, max_tokens = 1e3) %>% 
-  step_tfidf(summary)
-
-model <- svm_linear(mode="classification")
-
-wf <- workflow() %>% 
-  add_recipe(rec) %>% 
-  add_model(model)
-
-model_fit <- wf %>% 
-  fit(train_data)
-```
-
-```{r}
-test_data$prediction <- predict(model_fit, test_data)$.pred_class
-
-scorer <- metric_set( yardstick::accuracy, 
-                      yardstick::precision, 
-                      yardstick::recall, 
-                      yardstick::f_meas
-)
-
-scorer(test_data, truth=env, estimate=prediction, event_level="second")
-```
-
-```{r}
-#Prediction model to see if can predict if bill is focusing on health (as policy area)
-
-df2 <- df[sample(nrow(df)),]
-df2$env <- 0
-df2$env[df2$policy_area == "Health"] <- 1
-df2$env <- factor(df2$env)
-
-df_split <- initial_split(df2, prop=0.8) 
-train_data <- training(df_split) 
-test_data <- testing(df_split)
-
-rec <- recipe(env ~ summary, data = train_data) %>% 
-  step_tokenize(summary) %>% 
-  step_tokenfilter(summary, max_tokens = 1e3) %>% 
-  step_tfidf(summary)
-
-model <- svm_linear(mode="classification")
-
-wf <- workflow() %>% 
-  add_recipe(rec) %>% 
-  add_model(model)
-
-model_fit <- wf %>% 
-  fit(train_data)
-```
-
-```{r}
-test_data$prediction <- predict(model_fit, test_data)$.pred_class
-
-scorer <- metric_set( yardstick::accuracy, 
-                      yardstick::precision, 
-                      yardstick::recall, 
-                      yardstick::f_meas
-)
-
-scorer(test_data, truth=env, estimate=prediction, event_level="second")
-```
+## Conclusion

### 2022-11-30 draft_final_assingment.Rmd
Change

@@
 
-textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
-                   color = c("blue", "red"))
+textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300, color = c("green","orange","grey"))
 
@@
                    color = c("green","blue", "red"))
-```
-
-## Wordcloud comparing Democrats and Republicans
-
-```{r, wa }
-dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
-                     corp$party) %>%
-  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm_trim(min_termfreq = 3)
-
-textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
-                   color = c("green","blue", "red"))
-```
-
-## Wordcloud congress parties 115
-
-```{r, wa }
-
-corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
-modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
-   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm_trim(min_termfreq = 3)
-
-mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
-                   color = c("green","blue", "red"))
-mp15
-```
-
-## Wordcloud congress parties 116
-
-```{r, wa }
-
-corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
-modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
-  dfm_trim(min_termfreq = 3)
-
-mp16 <- textplot_wordcloud(modelpart16, comparison = TRUE, max_words = 300,
-                   color = c("green","blue", "red"))
-mp16
-
 ```

### 2022-12-01 summary_final_assingment.Rmd
final_push

--- 2022-11-30 draft_final_assingment.Rmd
@@
 ---
-title: "draft_final_assignment"
-author: "Andrew Wells"
+title: "Final assignment presentation"
+author: "Alexander Kraess, Andrew Wells, Julian Kath & Lorenzo Gini"
 date: "11/18/2022"
 output: 
-  html_document:
+  prettydoc::html_pretty:
+    theme: hpstr
+    hightlight: github
     toc: TRUE
-    theme: cosmo
-    toc_float: TRUE
 ---
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, warning=FALSE, message=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
+library(htmltools)
 library(tidyverse)
@@
 library(plotly)
+library(reticulate)
+library(igraph)
+library(rjson)
+library(visNetwork)
 ```
@@
 df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
+df_cosp <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/cosponsors_sponsors.csv")
+df_bills <- read_csv("data\\old_data\\all_bills.csv")
 head(df, 5)
@@
   theme_minimal()
+```
+
+## Policy fields
+
+```{r}
+fromJSON(file = "slides\\plots\\polar_line_plot") %>% plotly::as_widget()
 ```
@@
 
-textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300, color = c("green","orange","grey"))
+textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
+                   color = c("blue", "red"))
 
@@
 
+p <- ggplotly(p)
 p
-ggplotly(p)
 ```
@@
 
+j <- ggplotly(j)
 j
-ggplotly(j)
 ```
@@
 
+# Network graph of 116 House members
+
+```{r}
+df_labels <- df_cosp %>% 
+  inner_join(
+    df, 
+    by = c("number"= "bill number")
+  ) %>% 
+  inner_join(
+    df_bills %>% select(number, originChamber),
+    by = 'number'
+  ) %>% 
+  filter(session == 116, originChamber == 'House') %>% 
+  mutate(
+    cosponsor_name = str_replace_all(cosponsor_name, '\\w\\.\\s', ''),
+    cosponsor_name = str_replace_all(tolower(cosponsor_name), " ", "_"))
+
+df_labels %>% 
+  group_by(number) %>% 
+  summarize(cosps = paste(cosponsor_name, collapse = " ")) -> df_grouped
+
+corpus(df_grouped$cosps) %>% 
+  tokens() %>% 
+  fcm() %>% 
+  as.matrix() %>% 
+  graph_from_adjacency_matrix(mode = "undirected", weighted = T) %>% 
+  toVisNetworkData() -> visn
+
+visn$edges$value <- visn$edges$weight
+
+edges <- data.frame(visn$edges) %>% 
+  filter(weight > 25)
+nodes <- data.frame(visn$nodes) %>% 
+  left_join(df_labels %>% select(cosponsor_name, cosponsor_party) %>% distinct(), by = c('label' = 'cosponsor_name')) %>% 
+  filter(!duplicated(label)) %>% 
+  rename('group' = 'cosponsor_party') %>% 
+  mutate(color.background = if_else(group == "R",  "darkred", "darkblue"),
+         shadow = T,
+         font.color = 'black',
+         borderWidth = 2) %>% 
+  filter(label %in% edges$from | label %in% edges$to) %>% 
+  mutate(label = str_replace_all(label, '_',  ' ') %>% tools::toTitleCase(),
+         title = label)
+
+network <- visNetwork(nodes, edges) %>% 
+  visNodes(color = list(border = "darkgrey", 
+                        borderWidth = 2,
+                        highlight = list(border = 'darkgrey', background = 'orange'))
+           ) %>% 
+  visEdges(color = list(color = '#d3d3d3', highlight = 'orange')) %>% 
+  visPhysics(maxVelocity = 3)
+
+network
+```
+
 ## Topic modeling
 
+```{r}
+umap <- read.csv('data\\umap_projection_data.csv')
+
+umap %>% 
+  ggplot(aes(x, y, color = cosponsor_D_perc,
+             text = paste('Title:' , title, 
+                          '<br>Policy Area: ', policyarea, 
+                          '<br>Session: ', session, 
+                          '<br>Topic: ', cluster))) +  
+  geom_point() + 
+  scale_color_gradient2(midpoint = .5, name = "Democrat share") + 
+  theme_minimal() + 
+  labs(x = '', y = '', title = "UMAP Projection of US Congress bill summaries 115-117") +
+  theme(panel.background = element_rect(fill='#fbfbfb', colour='#fbfbfb')) -> p
+
+ggp <- ggplotly(p)
+
+ggp
+```
+
 ## Conclusion
+- In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
+- Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
+- There are some key actors that enable working across the aisle and are known for bipartisan collaboration

### 2022-12-01 summary_final_assingment.Rmd
edit_opening

@@
 
--   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:
+-   Between 2017 and 2022 there have been major shifts in terms of majorities in the US congress:
 
-    -   in 2016, both chambers were hold by Republicans
+    -   In the 115th Congress (Jan 2017 - Dec 2018), both chambers were hold by Republicans
 
-    -   in 2018, the Democrats gained a majority in Congress
+    -   In the 116th Congress (Jan 2019 - Dec 2020), the Democrats gained a majority in Congress, the Republicans remained in the majority in the Senate
 
-    -   in 2020 the Democrats gained Congress and Senate
+    -   In the 117th Congress (Jan 2021 - Dec 2022), the Democrats gained Congress and the Senate
 
@@
 
-We scraped our data from: https://data.gov/developers/apis/index.html
+We scraped our data from: <https://data.gov/developers/apis/index.html>
 
@@
 ## Density of cosponsors
+
 ```{r}
@@
 ## Conclusion
+
 -   In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics

### 2022-12-01 summary_final_assingment.Rmd
Update summary_final_assingment.Rmd

@@
   geom_point(color="grey", shape=21, size=0.5) + 
+  labs(title = "Dimensionality of all summary texts", x = "X", y = "Y",
+       fill = "Bill sponsorship", 
+       caption = "All bills represented, Democrat are bills with > 0.66 Democrat,
+       Republican are bills with > 0.66 Republican, Both are bills in between.") +
   scale_fill_manual(values=colordict) +
@@
   geom_point(color="grey", shape=21, size=0.5) + 
+    labs(title = "Dimensionality of partisan summary texts", x = "X", y = "Y",
+       fill = "Bill sponsorship",
+       caption = "Bills with only completely Democrat of 
+       Republican sponsorship represented.") +
   scale_fill_manual(values=colordict2) +
@@
 -   Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
+-   The dimensionality of texts is not systematically different between Democrat and Republican sponsored bills
+-   The sentiments of bills sponsored primarily by Democrats or Republicans does not seem correlated with the party in power
 -   There are some key actors that enable working across the aisle and are known for bipartisan collaboration

### 2022-12-01 summary_final_assingment.Rmd
Update summary_final_assingment.Rmd

--- 2022-12-01 summary_final_assingment.Rmd
@@
   tokens_wordstem() %>%
-  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
+  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
   dfm()
@@
 
-dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
   dfm_trim(min_termfreq = 3)
@@
 
-#Wordcloud congress 115
 ```
@@
 modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
-   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
   dfm_trim(min_termfreq = 3)
@@
 corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
-modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
+modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
   dfm_trim(min_termfreq = 3)
